\section{Sing}

% 第一页不使用页头
\thispagestyle{empty}

% 设置页眉为当前歌曲名
\fancyhead[L]{\small Sing}

\begin{spacing}{1.5}
\begin{flushleft}
It's late in the evening\\
\textit{夜色已深}\lyricspace

Glass on the side\\
\textit{酒杯放在一旁}\lyricspace

I've been sat with you\\
\textit{我整晚都和你坐在一起}\lyricspace

For most of the night\\
\textit{度过了大半个夜晚}\lyricspace

Ignoring everybody here\\
\textit{无视这里的每个人}\lyricspace

We wish they would disappear\\
\textit{我们希望他们消失}\lyricspace

So maybe we could get down now\\
\textit{这样我们或许可以开始狂欢}\lyricspace

And I don't wanna know\\
\textit{我不想知道}\lyricspace

If you're getting ahead of the program\\
\textit{你是否已经领先于计划}\lyricspace

I want you to be mine, lady\\
\textit{我想让你成为我的，女士}\lyricspace

To hold your body close\\
\textit{紧紧抱住你的身体}\lyricspace

Take another step into the no-man's land\\
\textit{再迈一步进入无人之地}\lyricspace

And for the longest time, lady\\
\textit{在很长一段时间里，女士}\lyricspace

I need you, darling\\
\textit{我需要你，亲爱的}\lyricspace

Come on, set the tone\\
\textit{来吧，定下基调}\lyricspace

If you feel you're falling\\
\textit{如果你感觉自己在坠落}\lyricspace

Won't you let me know?\\
\textit{你难道不让我知道吗？}\lyricspace

Oh, oh\\
\textit{哦，哦}\lyricspace

Oh, oh\\
\textit{哦，哦}\lyricspace

If you love me\\
\textit{如果你爱我}\lyricspace

Come on, get involved\\
\textit{来吧，参与进来}\lyricspace

Feel it rushing through you\\
\textit{感受它在你体内奔涌}\lyricspace

From your head to toe\\
\textit{从你的头到脚}\lyricspace

Oh, oh\\
\textit{哦，哦}\lyricspace

Oh, oh\\
\textit{哦，哦}\lyricspace

Sing!\\
\textit{唱吧！}\lyricspace

(Oh, oh)\\
\textit{（哦，哦）}\lyricspace

(Oh, oh)\\
\textit{（哦，哦）}\lyricspace

Louder!\\
\textit{大声点！}\lyricspace

(Oh, oh)\\
\textit{（哦，哦）}\lyricspace

Sing!\\
\textit{唱吧！}\lyricspace

(Oh, oh)\\
\textit{（哦，哦）}\lyricspace

This love is ablaze, I saw flames from the side of the stage\\
\textit{这份爱在燃烧，我从舞台侧面看到了火焰}\lyricspace

And the fire brigade comes in a couple of days\\
\textit{消防队几天后才会来}\lyricspace

Until then, we got nothing to say and nothing to know\\
\textit{在那之前，我们无话可说，也一无所知}\lyricspace

But something to drink and maybe something to smoke\\
\textit{但有些东西可以喝，也许还有些东西可以抽}\lyricspace

Let it go until our roads are changed\\
\textit{顺其自然，直到我们的道路改变}\lyricspace

Singing We Found Love in a local rave\\
\textit{唱着《我们在当地的狂欢派对上找到了爱》}\lyricspace

No, I don't really know what I'm supposed to say\\
\textit{不，我真的不知道该说什么}\lyricspace

But I can just figure it out, then hope and pray\\
\textit{但我可以想办法，然后希望和祈祷}\lyricspace

I told her my name, then said: It's nice to meet you\\
\textit{我告诉她我的名字，然后说：很高兴认识你}\lyricspace

Then she handed me a bottle of water filled with tequila\\
\textit{然后她递给我一瓶装满龙舌兰的水}\lyricspace

I already know if she's a keeper\\
\textit{我已经知道她是否值得留住}\lyricspace

Just from this one small act of kindness, I'm in\\
\textit{仅仅从这一小小的善举，我就深陷其中}\lyricspace

Deep shit if anybody finds out\\
\textit{如果有人发现，我就麻烦了}\lyricspace

I meant to drive home, but I drunk all of it now\\
\textit{我本打算开车回家，但现在我全喝光了}\lyricspace

Not sobering up, we just sit on the couch\\
\textit{没有清醒过来，我们只是坐在沙发上}\lyricspace

One thing led to another, now she's kissing my mouth\\
\textit{一件事导致另一件事，现在她在亲吻我的嘴}\lyricspace

I need you, darling\\
\textit{我需要你，亲爱的}\lyricspace

Come on, set the tone\\
\textit{来吧，定下基调}\lyricspace

If you feel you're falling\\
\textit{如果你感觉自己在坠落}\lyricspace

Won't you let me know?\\
\textit{你难道不让我知道吗？}\lyricspace

Oh, oh\\
\textit{哦，哦}\lyricspace

Oh, oh\\
\textit{哦，哦}\lyricspace

If you love me\\
\textit{如果你爱我}\lyricspace

Come on, get involved\\
\textit{来吧，参与进来}\lyricspace

Feel it rushing through you\\
\textit{感受它在你体内奔涌}\lyricspace

From your head to toe\\
\textit{从你的头到脚}\lyricspace

Oh, oh\\
\textit{哦，哦}\lyricspace

Oh, oh\\
\textit{哦，哦}\lyricspace

Sing!\\
\textit{唱吧！}\lyricspace

(Oh, oh)\\
\textit{（哦，哦）}\lyricspace

(Oh, oh)\\
\textit{（哦，哦）}\lyricspace

Louder!\\
\textit{大声点！}\lyricspace

(Oh, oh)\\
\textit{（哦，哦）}\lyricspace

Sing!\\
\textit{唱吧！}\lyricspace

(Oh, oh)\\
\textit{（哦，哦）}\lyricspace

(Can you feel it?)\\
\textit{（你能感觉到吗？）}\lyricspace

All the guys in here don't even wanna dance\\
\textit{这里的所有人甚至都不想跳舞}\lyricspace

(Can you feel it?)\\
\textit{（你能感觉到吗？）}\lyricspace

All that I can hear is music from the back\\
\textit{我能听到的只有后面的音乐}\lyricspace

(But can you feel it?)\\
\textit{（但你能感觉到吗？）}\lyricspace

Found you hiding here, so won't you take my hand, darling?\\
\textit{发现你躲在这里，所以你不牵我的手吗，亲爱的？}\lyricspace

Before the beat kicks in again\\
\textit{在节拍再次响起之前}\lyricspace

Can you feel it?\\
\textit{你能感觉到吗？}\lyricspace

Can you feel it?\\
\textit{你能感觉到吗？}\lyricspace

Oh, no, no, no, ow!\\
\textit{哦，不，不，不，噢！}\lyricspace

(Sing!) I need you, darling\\
\textit{（唱吧！）我需要你，亲爱的}\lyricspace

Come on, set the tone\\
\textit{来吧，定下基调}\lyricspace

If you feel you're falling\\
\textit{如果你感觉自己在坠落}\lyricspace

Won't you let me know?\\
\textit{你难道不让我知道吗？}\lyricspace

Louder! (Oh, oh)\\
\textit{大声点！（哦，哦）}\lyricspace

(Oh, oh)\\
\textit{（哦，哦）}\lyricspace

(Sing!) If you love me\\
\textit{（唱吧！）如果你爱我}\lyricspace

Come on, get involved\\
\textit{来吧，参与进来}\lyricspace

Feel it rushing through you\\
\textit{感受它在你体内奔涌}\lyricspace

From your head to toe\\
\textit{从你的头到脚}\lyricspace

(Louder!) (Oh, oh)\\
\textit{（大声点！）（哦，哦）}\lyricspace

(Oh, oh)\\
\textit{（哦，哦）}\lyricspace

Sing!\\
\textit{唱吧！}\lyricspace
\end{flushleft}
\end{spacing} 
